Open Set Logo Detection and Retrieval

### 2017-09-11 paper-final.tex
Final fixes and polishing for submission.

\author{{\large Paper ID 666??}}
%\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, Dieter Willersinn\sup{1}, J\"urgen Beyerer\sup{1,2}}
%\affiliation{\sup{1} Fraunhofer IOSB, Karlsruhe, Germany}
%\affiliation{\sup{2} Karlsruhe Institute of Technology KIT, Vision and Fusion Lab, Karlsruhe, Germany}
%\email{$\lbrace$andras.tuezkoe$|$christian.herrmann$|$daniel.manger$|$dieter.willersinn$\rbrace$@iosb.fraunhofer.de}
%%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
%}

@@

\abstract{
%%TODO write text here, 70-200 words
Current logo retrieval research focuses on closed set scenarios. We argue that the logo domain is too large for this strategy and requires an open set approach. To foster research in this direction, a large-scale logo dataset, called Logos in the Wild, is collected and released to the public.
A typical open set logo retrieval application is, for example, judging the effectiveness of advertisement in sports event broadcasts. Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a set of images or videos. Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption. Thus, an open set logo retrieval method is proposed in this work which allows searching for previously unfamiliar logos by a single query sample. A two stage concept with separate logo detection and comparison is proposed where both modules are based on task specific \acp{CNN}. If trained with the Logos in the Wild data, significant performance improvements are observed, especially compared with state-of-the-art closed set approaches.
%serves to train the modules with sufficient appropriate in-the-wild data. 
%The proposed method extends the application field in comparison to closed set approaches and significant improvements over baseline methods derived from these state-of-the-art closed set approaches are shown. 
}

@@

\section{\uppercase{Introduction}}
\label{sec:introduction}
%\noindent- sport event broadcasts \\
%- \ac{CNN}-based \\
%- separation of workflow into detection and comparison stage, similar to person/face re-id/retrieval \\
%- given as query: search image, not a logo class id or logo name \\
%- extension of the all-in-one architecture known from closed set logo retrieval \\
%
%- there exists a wide variety of different kinds of logos as large-scale datasets, such as METU with more than ?? different logo classes, indicate \\
%
%- task: find all occurrences of a query logo including typical variations, such as color inversions
%
%contributions: \\
%  - detection of any logo, not only predefined ones from training data \\
%  - open set logo retrieval system with search image as query \\
%  - introduction of novel logo dataset \\
\noindent Automated search for logos is a desirable task in visual image analysis.
A key application is the effectiveness measurement of advertisements. Being able to find all logos in images, that match a query, for example a logo of a specific company, allows to assess the visual frequency and prominence of logos in TV broadcasts. Typically, these broadcasts are sports events where sponsorship and advertisement is very common. 
This requires a flexible system where the query can be easily defined and switched according to the current task. Especially, also previously unseen logos should be found even if only one query sample is available.
%In general, open set retrieval is understood as finding instances of the same class in a database given a single instance from this class which has never been seen before. Usually classes originate from the same category with logos being an example. Thus, prior knowledge about this category can be used to build appropriate retrieval methods. In most applications this prior knowledge is given in shape of training data.
This requirement excludes basically all current logo retrieval approaches because they make a closed world assumption where all searched logos are known beforehand. Instead, this paper focuses on open set logo retrieval where only one sample image of a logo is available.

Consequently, a novel processing strategy for logo retrieval based on a logo detector and a feature extractor is proposed as illustrated in figure~\ref{fig:pipeline}. Similar strategies are known from other open set retrieval tasks, such as face or person retrieval~\cite{bauml2010,herrmann2015b}. Both, the detector and the extractor are task specific \acp{CNN}. For detection, the Faster R-CNN framework~\cite{ren2015} is employed and the extractor is derived from classification networks for the ImageNet challenge~\cite{deng2009}.
%
\begin{figure}[t]
  %\vspace{-0.2cm}
  \centering
  \includegraphics[width=\linewidth]{img/outline.png}
  \caption{Proposed logo retrieval strategy.}
  \label{fig:pipeline}
\end{figure}

The necessity for open set logo retrieval becomes obvious when having a look at the diversity and amount of existing logos and brands\footnote{The term brand is used in this work as synonym for a single logo class. Thus, a brand might also refer to a product or company name if an according logo exists.}. The METU trademark dataset~\cite{tursun2017} contains, for example, over half a million different brands. Given this number, a closed set approach where all different brands are pre-trained within the retrieval system is clearly inappropriate.
This is why our proposed feature extractor generates a discriminative logo descriptor, which generalizes to unseen logos, instead of a mere classification between previously known brands. The well-known high discriminative capabilities of \acp{CNN} allow to construct such a feature extractor.

One challenge for training a general purpose logo detector lies in appropriate training data. Many logo or trademark dataset~\cite{eakins1998,hoi2015,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application. The need for annotated logo bounding boxes in the images limits the number of suitable datasets. Existing logo datasets~\cite{joly2009,kalantidis2011,romberg2011,letessier2012,bianco2015,su2016,bianco2017} with available bounding boxes are often restricted to a very small number of brands and mostly high quality images. Especially, occlusions, blur and variations within a logo type are only partially covered.
To address these shortcomings, the novel Logos in the Wild dataset is collected and made publicly available~\footnote{\url{url://to.come}}.

@@

\section{\uppercase{Related Work}}
%\noindent- Logo Retrieval (\xie closed set approaches) \\
\noindent Current logo retrieval strategies are generally solving a closed set detection and classification problem. Eggert et.al. \cite{eggert2015} utilized \acp{CNN} to extract features from logos and determined their brand by classification with a set of \acp{SVM}. Fast R-CNN \cite{girshick2015} was used for the first time to retrieve logos from images by Iandola et al. \cite{iandola2015} and achieved superior results on the FlickrLogos-32 dataset \cite{romberg2011}. Furthermore, R-CNN, Fast R-CNN and Faster R-CNN were used in \cite{bao2016,oliveira2016,qi2017}. As closed set methods, all of them use the same brands for training as for validation.

@@

% Detector Frameworks: Faster R-CNN~\cite{ren2015}, SSD~\cite{liu2016b}, Yolo~\cite{redmon2016}, ...
\subsection{Object Detector Frameworks}
Early detectors applied hand-crafted features, such as Haar-like features, combined with a classifier to detect objects in images \cite{viola2004}. 
Nowadays, deep learning methods surpass the traditional methods by a significant margin. In addition, they allow a certain level of object classification within the detector which is mostly used to simultaneously detect different object categories, such as  persons and cars \cite{sermanet2013}. 
%The OverFeat framework uses sliding windows on multiple scales of the image and combines the \ac{CNN} features to detect objects and classify them. 
The YOLO detector \cite{redmon2015} introduces an end-to-end network for object detection and classification based on bounding box regressors for object localization. This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2016b}. 
Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a \ac{RPN} to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network. 
Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 6.6cm 0cm 0cm, clip]{img/openset.pdf}%
\caption{Comparison of closed and open set logo retrieval strategy.}%
\label{fig:openClosedSet}
\end{figure*}%

@@

\begin{table*}[t]
\centering
\caption{Publicly available in-the-wild logo datasets in comparison with the novel Logos in the Wild dataset.}
\label{tab:logoDatasets}
\begin{small}
\begin{tabular}{cl|ccc}
& \multicolumn{1}{c|}{\textbf{dataset}} & \textbf{brands} & \textbf{logo images} & \textbf{RoIs} \bigstrut[b]\\
\hline
\multirow{8}{*}{\vertboxs{public}} & BelgaLogos \cite{joly2009,letessier2012} & 37 & 1,321 & 2,697 \bigstrut[t] \\
& FlickrBelgaLogos \cite{letessier2012} & 37 & 2,697 & 2,697 \\
& Flickr Logos 27 \cite{kalantidis2011} & 27 & 810 & 1,261 \\
& FlickrLogos-32 \cite{romberg2011} & 32 & 2,240 & 3,404 \\
& Logos-32plus \cite{bianco2015,bianco2017} & 32 & 7,830 & 12,300 \\
& TopLogo10 \cite{su2016} & 10 & 700 & 863 \bigstrut[b] \\
\cline{2-5}
& combined & 80 (union) & 15,598 & 23,222 \bigstrut \\
\hline
%\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 868 & 11,039 & 32,808 \bigstrut[t]
\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 871 & 11,054 & 32,850 \bigstrut[t]
\end{tabular}
\end{small}
\end{table*}
%
\section{\uppercase{Logo Detection}}
%\noindent- class agnostic detector \\
%- different base networks: VGG-CNN-M, VGG16
\noindent The current state-of-the-art approaches for scene retrieval create a global feature of the input image. This is achieved by either inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature \cite{torii2015,arandjelovic2016,kalantidis2016}. For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects. Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval applications.

Therefore, we choose a two-stage approach consisting of logo detection and logo classification as figure~\ref{fig:openClosedSet} illustrates for the open set case. First, the logos have to be detected in the input image. 
Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straight forward baseline method.
Other state-of-the-art detector options, such as SSD \cite{liu2016b} or YOLO \cite{redmon2016}, potentially offer a faster detection at the cost of detection performance \cite{huang2016b}.

@@

\section{\uppercase{Logo Comparison}}
\noindent After logos are detected, the correspondences to the query sample have to be searched. 
For logo retrieval, features are extracted from the detected logos for comparison with the query sample. Thus, the logo feature vectors for the query image and the ones for the database are collected and normalized. Pair-wise comparison is then performed by cosine similarity.

@@

Altogether, the proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network. This setup is advantageous for the quality of the extracted logo features because the extractor network has only to focus on a specific region.
This is an improvement compared to including both logo detection and comparison in the regular Faster R-CNN framework which lacks generalization to unseen classes. We argue that the specialization in the regular Faster R-CNN to the limited number of specific brands in the training set does not cover the complexity and breadth of the logo domain. This is why a separate and more elaborate feature extractor is proposed even though this might appear like a less elegant solution.

%
\setlength{\frameSize}{3.7cm}
\begin{figure*}%
\centering%
\includegraphics[height=\frameSize]{img/sample2.png}
\hfill
\includegraphics[height=\frameSize]{img/sample12.png}
\hfill
\includegraphics[height=\frameSize]{img/sample3.png}%
\\
\vspace{1.5mm}%
\includegraphics[height=\frameSize]{img/sample15.png}
\hfill
\includegraphics[height=\frameSize]{img/sample5.png}
\hfill
\includegraphics[height=\frameSize]{img/sample9.png}
\caption{Examples from the collected Logos in the Wild dataset.}%
\label{fig:logoSamples}
\end{figure*}%
%
\section{\uppercase{Logo Dataset}}
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
\caption{Annotations differentiate between textual and graphical logos.}%
\label{fig:annotatedSample}
\end{figure}%
%
\noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets. A comparison to other public in-the-wild datasets with annotated bounding boxes is given in table~\ref{tab:logoDatasets}.
The goal is an in-the-wild logo dataset with images including logos instead of the raw original logo graphics. In addition, images where the logo represents only a minor part of the image are preferred. See figure~\ref{fig:logoSamples} for a few examples of the collected data.
Following the general suggestions from \cite{bansal2017}, we target for a dataset containing significantly more brands instead of collecting additional image samples for the already covered brands. This is the exact opposite strategy than performed by the Logos-32plus dataset.
Starting with a list of well-known brands and companies, an image web search is performed. Because most other web collected logo datasets mainly rely on Flickr, we opt for Google image search to broaden the domain. Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `advertisement', `building', `poster' or `store'.

For each search result, the first $N$ images are downloaded, where $N$ is determined by a quick manual inspection to avoid collecting too much garbage. 
%All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one manually annotated with logo bounding boxes or sorted out if unsuitable.
Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics. Taken pictures of such logos and advertisement posters on the other hand are desired to be in the dataset. 
Annotations distinguish between textual and graphical logos as well as different logos from one company as exemplary indicated in figure~\ref{fig:annotatedSample}.
Altogether, the current version of the dataset, contains 871 brands with 32,850 annotated bounding boxes. 238 brands occur at least 10 times. An image may contain several logos with the maximum being 118 logos in one image. The full distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}.

@@

\section{\uppercase{Experiments}}
%\noindent- explain FROC curve \\
%- maybe introduce mAP \\
%- explain baseline method(s) \\
%concepts/desired experiments \\
%- train on public non-Flickr brands \\
%- additionally train on own logo dataset \\
%- test on FlickrLogos-32 test datasets \\
%
%- additional evaluation on own SportsLogos dataset and qualitative results \\
\noindent The proposed method is evaluated on the test set benchmark of the public FlickrLogos-32 dataset including the distractors. Additional application specific experiments are performed on an internal dataset of sports event TV broadcasts. 
The training set consists of two parts. The union of all public logo datasets as listed in table~\ref{tab:logoDatasets} and the novel \ac{LitW} dataset. For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data. 10 percent of the remaining images are set aside for network validation in each case. This results in the final training and test set sizes listed in table~\ref{tab:trainTestStatistics}.
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{Train and test set statistics.}
\label{tab:trainTestStatistics}
\begin{small}
% Table generated by Excel2LaTeX from sheet 'Tabelle1'
\begin{tabular}{cl|cc}
\textbf{phase} & \multicolumn{1}{c|}{\textbf{data}} & \multicolumn{1}{c}{\textbf{brands}} & \multicolumn{1}{c}{\textbf{RoIs}} \bigstrut[b]\\
\hline
\multirow{2}[2]{*}{train} & public & 47    & 3,113 \bigstrut[t]\\
      & public+\ac{LitW} v1.0 & 632   & 18,960 \bigstrut[b]\\
\hline
test  & FlickrLogos-32 test & 32    & 1,602 \bigstrut[t]\\
\end{tabular}%
\end{small}
\endgroup
\end{table}

@@

\subsection{Detection}
As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
It is naively adapted to open set detection by using the \ac{RPN} scores as detections. This skips the closed set classification part of the network which is trained on different logos than should be detected on the test set.
The proposed brand agnostic logo detector is first trained on the same public data for comparison. All Faster R-CNN detectors are based on the VGG16 network.
The results in figure~\ref{fig:detectionFroc} indicate that the proposed brand agnostic strategy is superior by a significant margin. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
\caption{Detection FROC curves for the FlickrLogos-32 test set.}%
\label{fig:detectionFroc}
\end{figure}%
%

>>>>

\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, J\"urgen Beyerer\sup{1,2}}
\affiliation{\sup{1} Fraunhofer IOSB, Karlsruhe, Germany}
\affiliation{\sup{2} Karlsruhe Institute of Technology KIT, Vision and Fusion Lab, Karlsruhe, Germany}
\email{$\lbrace$andras.tuezkoe$|$christian.herrmann$|$daniel.manger$|$juergen.beyerer$\rbrace$@iosb.fraunhofer.de}
%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
}
%\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, Dieter Willersinn\sup{1}, J\"urgen Beyerer\sup{1,2}}
%\affiliation{\sup{1} Fraunhofer IOSB, Karlsruhe, Germany}
%\affiliation{\sup{2} Karlsruhe Institute of Technology KIT, Vision and Fusion Lab, Karlsruhe, Germany}
%\email{$\lbrace$andras.tuezkoe$|$christian.herrmann$|$daniel.manger$|$dieter.willersinn$\rbrace$@iosb.fraunhofer.de}
%%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
%}

@@

\abstract{
%%TODO write text here, 70-200 words
Current logo retrieval research focuses on closed set scenarios. We argue that the logo domain is too large for this strategy and requires an open set approach. To foster research in this direction, a large-scale logo dataset, called Logos in the Wild, is collected and released to the public.
A typical open set logo retrieval application is, for example, assessing the effectiveness of advertisement in sports event broadcasts. Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a set of images or videos. Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption. Thus, an open set logo retrieval method is proposed in this work which allows searching for previously unseen logos by a single query sample. A two stage concept with separate logo detection and comparison is proposed where both modules are based on task specific \acp{CNN}. If trained with the Logos in the Wild data, significant performance improvements are observed, especially compared with state-of-the-art closed set approaches.
%serves to train the modules with sufficient appropriate in-the-wild data. 
%The proposed method extends the application field in comparison to closed set approaches and significant improvements over baseline methods derived from these state-of-the-art closed set approaches are shown. 
}

@@

\section{\uppercase{Introduction}}
\label{sec:introduction}
%\noindent- sport event broadcasts \\
%- \ac{CNN}-based \\
%- separation of workflow into detection and comparison stage, similar to person/face re-id/retrieval \\
%- given as query: search image, not a logo class id or logo name \\
%- extension of the all-in-one architecture known from closed set logo retrieval \\
%
%- there exists a wide variety of different kinds of logos as large-scale datasets, such as METU with more than ?? different logo classes, indicate \\
%
%- task: find all occurrences of a query logo including typical variations, such as color inversions
%
%contributions: \\
%  - detection of any logo, not only predefined ones from training data \\
%  - open set logo retrieval system with search image as query \\
%  - introduction of novel logo dataset \\
\noindent Automated search for logos is a desirable task in visual image analysis.
A key application is the effectiveness measurement of advertisements. Being able to find all logos in images that match a query, for example, a logo of a specific company, allows to assess the visual frequency and prominence of logos in TV broadcasts. Typically, these broadcasts are sports events where sponsorship and advertisement is very common. 
This requires a flexible system where the query can be easily defined and switched according to the current task. Especially, also previously unseen logos should be found even if only one query sample is available.
%In general, open set retrieval is understood as finding instances of the same class in a database given a single instance from this class which has never been seen before. Usually classes originate from the same category with logos being an example. Thus, prior knowledge about this category can be used to build appropriate retrieval methods. In most applications this prior knowledge is given in shape of training data.
This requirement excludes basically all current logo retrieval approaches because they make a closed world assumption in which all searched logos are known beforehand. Instead, this paper focuses on open set logo retrieval where only one sample image of a logo is available.

Consequently, a novel processing strategy for logo retrieval based on a logo detector and a feature extractor is proposed as illustrated in figure~\ref{fig:pipeline}. Similar strategies are known from other open set retrieval tasks, such as face or person retrieval~\cite{bauml2010,herrmann2015b}. Both, the detector and the extractor are task specific \acp{CNN}. For detection, the Faster R-CNN framework~\cite{ren2015} is employed and the extractor is derived from classification networks for the ImageNet challenge~\cite{deng2009}.
%
\begin{figure}[t]
  %\vspace{-0.2cm}
  \centering
  \includegraphics[width=\linewidth, trim=0cm 25.4cm 0cm 0cm, clip]{img/outline.pdf}
  \caption{Proposed logo retrieval strategy.}
  \label{fig:pipeline}
\end{figure}
%%
%\begin{figure}[t]
%  %\vspace{-0.2cm}
%  \centering
%  \includegraphics[width=\linewidth]{img/outline.png}
%  \caption{Proposed logo retrieval strategy.}
%  \label{fig:pipeline}
%\end{figure}

The necessity for open set logo retrieval becomes obvious when considering the diversity and amount of existing logos and brands\footnote{The term \textit{brand} is used in this work as synonym for a single logo class. Thus, a brand might also refer to a product or company name if an according logo exists.}. The METU trademark dataset~\cite{tursun2017} contains, for example, over half a million different brands. Given this number, a closed set approach where all different brands are pre-trained within the retrieval system is clearly inappropriate.
This is why our proposed feature extractor generates a discriminative logo descriptor, which generalizes to unseen logos, instead of a mere classification between previously known brands. The well-known high discriminative capabilities of \acp{CNN} allow to construct such a feature extractor.

One challenge for training a general purpose logo detector lies in appropriate training data. Many logo or trademark datasets~\cite{eakins1998,hoi2015,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application. The need for annotated logo bounding boxes in the images limits the number of suitable available datasets. Existing logo datasets~\cite{joly2009,kalantidis2011,romberg2011,letessier2012,bianco2015,su2016,bianco2017} with available bounding boxes are often restricted to a very small number of brands and mostly high quality images. Especially, occlusions, blur and variations within a logo type are only partially covered.
To address these shortcomings, we collect the novel Logos in the Wild dataset and make it publicly available~\footnote{\url{url://to.come}}.

@@

\section{\uppercase{Related Work}}
%\noindent- Logo Retrieval (\xie closed set approaches) \\
\noindent Current logo retrieval strategies are generally solving a closed set detection and classification problem. Eggert et.al. \cite{eggert2015} utilized \acp{CNN} to extract features from logos and determined their brand by classification with a set of \acp{SVM}. Fast R-CNN \cite{girshick2015} was used for the first time to retrieve logos from images by Iandola et al. \cite{iandola2015} and achieved superior results on the FlickrLogos-32 dataset \cite{romberg2011}. Furthermore, R-CNN, Fast R-CNN and Faster R-CNN were used in \cite{bao2016,oliveira2016,qi2017}. As closed set methods, all of them use the same brands both for training and for validation.

@@

% Detector Frameworks: Faster R-CNN~\cite{ren2015}, SSD~\cite{liu2016b}, Yolo~\cite{redmon2016}, ...
\subsection{Object Detector Frameworks}
Early detectors applied hand-crafted features, such as Haar-like features, combined with a classifier to detect objects in images \cite{viola2004}. 
Nowadays, deep learning methods surpass the traditional methods by a significant margin. In addition, they allow a certain level of object classification within the detector which is mostly used to simultaneously detect different object categories, such as  persons and cars \cite{sermanet2013}. 
%The OverFeat framework uses sliding windows on multiple scales of the image and combines the \ac{CNN} features to detect objects and classify them. 
The YOLO detector \cite{redmon2015} introduces an end-to-end network for object detection and classification based on bounding box regressors for object localization. This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2016b}. 
The work on Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a \ac{RPN} to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network. 
Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 6.6cm 0cm 0cm, clip]{img/openset.pdf}%
\caption{Comparison of closed and open set logo retrieval strategy.}%
\label{fig:openClosedSet}
\end{figure*}%

@@

\begin{table*}[t]
\centering
\caption{Publicly available in-the-wild logo datasets in comparison with the novel Logos in the Wild dataset.}
\label{tab:logoDatasets}
\begin{small}
\begin{tabular}{cl|ccc}
& \multicolumn{1}{c|}{\textbf{dataset}} & \textbf{brands} & \textbf{logo images} & \textbf{RoIs} \bigstrut[b]\\
\hline
\multirow{8}{*}{\vertboxs{public}} & BelgaLogos \cite{joly2009,letessier2012} & 37 & 1,321 & 2,697 \bigstrut[t] \\
& FlickrBelgaLogos \cite{letessier2012} & 37 & 2,697 & 2,697 \\
& Flickr Logos 27 \cite{kalantidis2011} & 27 & 810 & 1,261 \\
& FlickrLogos-32 \cite{romberg2011} & 32 & 2,240 & 3,404 \\
& Logos-32plus \cite{bianco2015,bianco2017} & 32 & 7,830 & 12,300 \\
& TopLogo10 \cite{su2016} & 10 & 700 & 863 \bigstrut[b] \\
\cline{2-5}
& combined & 80 (union) & 15,598 & 23,222 \bigstrut \\
\hline
%\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 868 & 11,039 & 32,808 \bigstrut[t]
\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 871 & 11,054 & 32,850 \bigstrut[t]
\end{tabular}
\end{small}
\end{table*}
%
\section{\uppercase{Logo Detection}}
\label{sec:detection}
%\noindent- class agnostic detector \\
%- different base networks: VGG-CNN-M, VGG16
\noindent The current state-of-the-art approaches for scene retrieval create a global feature of the input image. This is achieved by either inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature \cite{torii2015,arandjelovic2016,kalantidis2016}. For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects. Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval applications.

Therefore, we choose a two-stage approach consisting of logo detection and logo classification as figure~\ref{fig:openClosedSet} illustrates for the open set case. First, the logos have to be detected in the input image. 
Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straightforward baseline method.
Other state-of-the-art detector options, such as SSD \cite{liu2016b} or YOLO \cite{redmon2016}, potentially offer a faster detection at the cost of detection performance \cite{huang2016b}.

@@

\section{\uppercase{Logo Comparison}}
\noindent After logos are detected, the correspondences to the query sample have to be searched. 
For logo retrieval, features are extracted from the detected logos for comparison with the query sample. Then, the logo feature vector for the query image and the ones for the database are collected and normalized. Pair-wise comparison is then performed by cosine similarity.

@@

Altogether, the proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network. This setup is advantageous for the quality of the extracted logo features because the extractor network has only to focus on a specific region.
This is an improvement compared to including both logo detection and comparison in the regular Faster R-CNN framework which lacks generalization to unseen classes. We argue that the specialization in the regular Faster R-CNN to the limited number of specific brands in the training set does not cover the complexity and breadth of the logo domain. This is why a separate and more elaborate feature extractor is proposed. % even though this might appear like a less elegant solution.

%
\setlength{\frameSize}{3.7cm}
\begin{figure*}%
\centering%
\includegraphics[height=\frameSize]{img/sample2.png}
\hfill
\includegraphics[height=\frameSize]{img/sample12.png}
\hfill
\includegraphics[height=\frameSize]{img/sample3.png}%
\\
\vspace{1.5mm}%
\includegraphics[height=\frameSize]{img/sample15.png}
\hfill
\includegraphics[height=\frameSize]{img/sample5.png}
\hfill
\includegraphics[height=\frameSize]{img/sample9.png}
\caption{Examples from the collected Logos in the Wild dataset.}%
\label{fig:logoSamples}
\end{figure*}%
%
\section{\uppercase{Logo Dataset}}
\noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets. A comparison to other public in-the-wild datasets with annotated bounding boxes is given in table~\ref{tab:logoDatasets}.
The goal is an in-the-wild logo dataset with images including logos instead of the raw original logo graphics. In addition, images where the logo represents only a minor part of the image are preferred. See figure~\ref{fig:logoSamples} for a few examples of the collected data.
Following the general suggestions from \cite{bansal2017}, we target for a dataset containing significantly more brands instead of collecting additional image samples for the already covered brands. This is the exact opposite strategy than performed by the Logos-32plus dataset.
Starting with a list of well-known brands and companies, an image web search is performed. Because most other web collected logo datasets mainly rely on Flickr, we opt for Google image search to broaden the domain. Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `advertisement', `building', `poster' or `store'. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
\caption{Annotations differentiate between textual and graphical logos.}%
\label{fig:annotatedSample}
\end{figure}%
%

For each search result, the first $N$ images are downloaded, where $N$ is determined by a quick manual inspection to avoid collecting too many irrelevant images. 
%All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one manually annotated with logo bounding boxes or sorted out if unsuitable.
Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics. Taken pictures of such logos and advertisement posters on the other hand are desired to be in the dataset. 
Annotations distinguish between textual and graphical logos as well as different logos from one company as exemplary indicated in figure~\ref{fig:annotatedSample}.
Altogether, the current version of the dataset, contains 871 brands with 32,850 annotated bounding boxes. 238 brands occur at least 10 times. An image may contain several logos with the maximum being 118 logos in one image. The full distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}.

@@

\section{\uppercase{Experiments}}
%\noindent- explain FROC curve \\
%- maybe introduce mAP \\
%- explain baseline method(s) \\
%concepts/desired experiments \\
%- train on public non-Flickr brands \\
%- additionally train on own logo dataset \\
%- test on FlickrLogos-32 test datasets \\
%
%- additional evaluation on own SportsLogos dataset and qualitative results \\
\noindent The proposed method is evaluated on the test set benchmark of the public FlickrLogos-32 dataset including the distractors. Additional application specific experiments are performed on an internal dataset of sports event TV broadcasts. 
The training set consists of two parts. The union of all public logo datasets as listed in table~\ref{tab:logoDatasets} and the novel \ac{LitW} dataset. For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data. Ten percent of the remaining images are set aside for network validation in each case. This results in the final training and test set sizes listed in table~\ref{tab:trainTestStatistics}.
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{Train and test set statistics.}
\label{tab:trainTestStatistics}
\begin{small}
% Table generated by Excel2LaTeX from sheet 'Tabelle1'
\begin{tabular}{cl|cc}
\textbf{phase} & \multicolumn{1}{c|}{\textbf{data}} & \multicolumn{1}{c}{\textbf{brands}} & \multicolumn{1}{c}{\textbf{RoIs}} \bigstrut[b]\\
\hline
\multirow{2}[2]{*}{train} & public & 47    & 3,113 \bigstrut[t]\\
      & public+\ac{LitW} v1.0 & 632   & 18,960 \bigstrut[b]\\
\hline
test  & FlickrLogos-32 test & 32    & 1,602 \bigstrut[t]\\
\end{tabular}%
\end{small}
\endgroup
\end{table}

@@

\subsection{Detection}
As indicated in section~\ref{sec:detection}, the baseline is the state-of-the-art closed set logo retrieval method from~\cite{su2016} which is trained on the public data and naively adapted to open set detection by using the \ac{RPN} scores as detections
%As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
%It is naively adapted to open set detection by using the \ac{RPN} scores as detections. This skips the closed set classification part of the network which is trained on different logos as should be detected on the test set.
The proposed brand agnostic logo detector is first trained on the same public data for comparison. All Faster R-CNN detectors are based on the VGG16 network.
The results in figure~\ref{fig:detectionFroc} indicate that the proposed brand agnostic strategy is superior by a significant margin. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
\caption{Detection FROC curves for the FlickrLogos-32 test set.}%
\label{fig:detectionFroc}
\end{figure}%
%
